---
title: "Metadata Requests"
author: "Juliano Palacios Abrantes"
date: "30/8/2017"
output: html_document
---


## Dr. Blanca Idalia Gutierez | CINVESTAV-Mérida
### Aug 30th, 2017

Correo: bigzzg@gmail.com

¿ya tienes ubicadas a las instituciones que están haciendo o han hecho trabajo de monitoreo en el golfo mexicano? Nos están pidiendo organizar una reunión con instituciones que hagan o hicieron monitoreo en el golfo, porque necesitamos esté relacionado con los índices que vamos a trabajor. Principalmente de componentes de calidad del agua y contaminacion, pero cualquier tipo de información sirve


```{r Blaca, eval=F, echo = T, message= F, warning = F}
library(data.table)
library(dplyr)

Idalia <- fread("~/Documents/Github/Meta_Data_Mexico/App/Template_4.1.csv")

Idalia_Data <- Idalia %>% 
  filter(Area =="Atlantic") %>% 
  group_by(Author,
           Institution,
           Research_Field,
           Reference,
           Compilation_Title) %>% 
  summarise(
    n=n(),
    MMID = paste(MMID, collapse = ";")
  ) %>% 
  select(-n)

write.csv(Idalia_Data,
          "Metadatos_Atlantico_Idalia.csv",
          row.names = F)

Autores_Fuera <- c(
  "CONAPESCA",
  "CONABIO"
)

National_Data <-Idalia %>% 
  filter(Area =="National") %>%
  filter(!Author %in% Autores_Fuera) %>% 
  group_by(Author,
           Institution,
           Research_Field,
           Reference,
           
           Compilation_Title) %>% 
  summarise(
    n=n(),
    MMID = paste(MMID, collapse = ";")
  ) %>% 
  select(-n)

write.csv(Idalia_Data,
          "Metadatos_Nacional_Idalia.csv",
          row.names = F)

```


## Bárbara Rojas; CONABIO
### Sep 27th, 2017

Correo: barbara.rojas@conabio.gob.mx

ANPs de interés para el proyecto son:
-PN Arrecifes de Puerto Morelos
-Parque Nacional Costa Occidental de Isla Mujeres, Punta Cancún y Punta Nizuc 
-APFF Manglares de Nichupté
-APFF Laguna de Términos
-RB Archipiélago de Revillagigedo
-RB Zona marina Bahía de los Ángeles, canales de Ballenas y de Salsipuedes
-PN Zona marina del Archipiélago de San Lorenzo
-RB Isla San Pedro Mártir

```{r Blaca, eval=F, echo = T, message= F, warning = F}
library(data.table)
library(dplyr)

Listado <- c(
  "Arrecifes de Puerto Morelos",
  "Isla Mujeres",
  "Punta Cancun",
  "Punta Nizuc", 
  "Nichupte",
  "Terminos",
  "Archipielago de Revillagigedo",
  "Revillagigedo",
  "Bahia de los Angeles",
  "Salsipuedes",
  "Archipielago de San Lorenzo",
  "San Lorenzo",
  "San Pedro Martir"
)


Barbara <- fread("~/Documents/Github/Meta_Data_Mexico/App/Template_4.1.csv")

Datos_in_Loc <- Barbara %>% 
  filter(grepl(
      paste(Listado, collapse="|"), 
      Location))

Datos_in_k <- Barbara %>% 
    filter(grepl(
      paste(Listado, collapse="|"), 
      Keywords))

#Check for repetition of Rows
Repeated <- Datos_in_k %>% 
  semi_join(Datos_in_Loc,
            by="MMID")

Datos_Barbara <- Datos_in_k %>% 
  filter(!MMID %in% Repeated$MMID) %>% #Removes repeated values
  bind_rows(Datos_in_Loc)

write.csv(Datos_Barbara,
          "Metadatos_ANP.csv",
          row.names = F)
                      

Datos_Barbara_Res <- Datos_in_k %>% 
  filter(!MMID %in% Repeated$MMID) %>% #Removes repeated values
  bind_rows(Datos_in_Loc) %>% 
  group_by(Compilation_Title,
           Dataset_Title,
           Author,
           Institution) %>% 
  summarise(Numero_de_Registros= n(),
            MMIDs = paste(MMID, collapse="; ")
            )

write.csv(Datos_Barbara_Res,
          "Metadatos_ANP_resumidos.csv",
          row.names = F)

```

## Dr. Ray Hilborn | UW
### Oct 18th, 2017

Dear Mr. Juliano E. Palacios Abrantes,

We are conducting a survey of how fisheries are managed around the world and have published our initial results in the attached paper. We would like very much to get individuals familiar with Mexico fisheries to complete a survey for one or more of the various species listed in the attached spreadsheet for Mexico. Ideally these individuals would come from different backgrounds, science, management, industry, NGO etc.

Please let me know if you might be able to provide contacts and perhaps an email introduction. If you are willing to complete a survey, please let me know that as well and for which species. 

```{r Hilborn, eval=F, echo = T, message= F, warning = F}
library(data.table)
library(dplyr)

Template <- fread("~/Documents/Github/Meta_Data_Mexico/App/Template_4.1.csv")
Ray <- read.csv("Species_List_Hilborn.csv")

Ignorar <- c(
  "James Simons; James.Simons@tamucc.edu",
  "Jorrit Poelen; jhpoelen@xs4all.nl",
  "Sky Bristol; sbristol@usgs.gov, Abby Benson; albenson@usgs.gov",
  "onia Alejandra Careaga Olvera; scareaga@conabio.gob.mx",
  "uenlace@conapesca.gob.mx"
)

Sci_Name <- Template %>% 
  filter(Subject_name %in% Ray$Subject_name) %>% 
  group_by(Subject_name,
           User_Contact) %>% 
  summarise(n=n()) %>% 
  filter(!User_Contact %in% Ignorar) %>% 
  filter(!is.na(User_Contact)) 


  Ray_Final <- Ray %>% 
    left_join(Sci_Name,
            by ="Subject_name")
  
  #### Merida ####
  
  # Jorge Lopez #
  Jorge_Lopez <- read_csv("~/Documents/Dropbox/Metadata_Mexico/Datasets/SISAL/Finalizados/Jorge_Lopez.csv")
  
Sci_Name_Jor <- Jorge_Lopez %>% 
  filter(Subject_name %in% Ray$Subject_name) %>% 
  group_by(Subject_name,
           User_Contact) %>% 
    summarise(n=n()) %>% 
    filter(!is.na(User_Contact)) %>% 
    bind_rows(Ray_Final) %>% 
  select(Subject_name,
         Taxonomic.Group,
         FAO.Spanish.Name,
         English.Name,
         Comments,
         everything(),
         -n
         ) %>% 
  rename(Scientific.Group=Subject_name)
  
write.csv(Sci_Name_Jor,
          "Hilborn_Dataset_JEPA.csv",
          row.names = FALSE)


``````
