---
title: "GloBI data"
author: "Juliano Palacios Abrantes"
date: "4/13/2017"
output:
  html_document: 
    keep_md: yes
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyr)
library(data.table)
library("sp") 
library(ggmap)
# Rglobi library
#devtools::install_github("ropensci/rglobi")
library(rglobi)
library(ggplot2)

#Spatial stuff
library("rgdal") # for ogrInfo() and readOGR()
library("tools") # for file_path_sans_ext()
#Reads GloBi data

# Data <- fread("Data/taxonCache.tsv",
#               header = TRUE
# )

# Read 1007695 rows and 9 (of 9) columns from 0.452 GB file in 00:00:06

```

# Introduction

This script was made to incorporate [GLoBI](http://www.globalbioticinteractions.org) data to the [Metadata](https://jepa.shinyapps.io/marmetadatamexeng/).

It uses the package rglobi to take data from GloBI taxa [reference](http://www.globalbioticinteractions.org/references) list and aggregate them by species (154,257 taxa).

## Isolate marine organisms

The way I came to isolate marine-related species was to delimit the species to Mexico's EEZ area.

```{r Mexico EEZ, echo=FALSE, eval =F}

# Load Mexico's EEZs 
# Data from (http://www.marineregions.org/downloads.php)

# The path
path_eez_world <- ("/Users/jpalacios/Documents/Box Sync/UBC/Oceans_Project/Distribution/Old_Data/World_EEZ_v8_2014")
#The File
fnam_eez_world <- "World_EEZ_v8_2014_HR.shp"
#Load it!
eez_world <- readOGR(dsn = path_eez_world,
                     layer =file_path_sans_ext(fnam_eez_world))

#Fortify function to get a data.frame
fortify.shape <- function(x){
  x@data$id <- rownames(x@data)
  x.f = fortify(x, region = "id")
  x.join <- inner_join(x.f, x@data, by = "id")
}

#### The actual EEZ ####

# Extract the EEZ for Mexico:
eez_p <- eez_world[eez_world@data$Country == "Mexico", ]

# Fortify the shapefile data:
eez_p <- fortify(eez_p)

# Get Mexico's EEZ
eez_Mex <- eez_p %>% 
  filter(piece == 1 | # Pacific side
           piece == 2) # Atlantic Side

#write.csv(eez_Mex, "eez_Mex.csv")

#### Check Step ####
# Just checking It is the map we want
# Pacific <-  Piece 1
# Atlantic <- Piece 2
# ggplot() +
#   geom_path(data = filter(eez_Mex,
#                           piece == 2),
#             aes(x = long,
#                 y = lat,
#                 group = group),
#             colour = "red", size = 0.75)

#____________________________Check End_____________________________#

```

```{r Part 2, echo =T, eval=T }

EEZ_Mex <- fread("./Data/eez_Mex.csv")


# Get all taxa on the list (From WoRMS; http://www.marinespecies.org/aphia.php?p=browser)
Taxa <- c(
  "Animalia",
  "Archea",
  "Bacteria",
  "Chromista",
  "Fungi",
  "Monera",
  "Plantae",
  "Protozoa",
  "Viruses"
)

#Set an initial subset for the GloBi data
Lat_N  <-  35 #Latitude_North
Lat_S  <-  15 #Latitude_South
Long_W <- -122 #Longitude_West
Long_E <- -90 #Longitude_East

# First Subset: Get all species interactions from GloBi within that first Area

# Don't know how to import all so will just make a function for it:
import.fun <- function(Taxa){
for (i in 1:length(Taxa)){ 
  
  x <- get_interactions_by_taxa(
    sourcetaxon = Taxa[i],
    bbox = c(
      Long_W,
      Lat_S,
      Long_E,
      Lat_N
    ),
    returnobservations = T
  )
Name <- paste(Taxa[i])
  assign( x = Name, value = x, envir = .GlobalEnv)
}
 # return(Name)
}

#____ End Function _____________________________________#

#Call function
import.fun(Taxa)

#Join everything in one single table
Subset_One <- bind_rows(Animalia,
                         Bacteria,
                         Chromista,
                         Fungi,
                         Plantae,
                         Protozoa,
                         Viruses)


### Second subset (Inside EEZ) ####
#From that initial subset (Subset_One), mark those that are located within Mexico's EEZ

In_EEZ_Mex <-data.frame(point.in.polygon(Subset_One$longitude,
                                    Subset_One$latitude,
                                    EEZ_Mex$long,
                                    EEZ_Mex$lat))
colnames(In_EEZ_Mex) <- "EEZ"

#Note <- 1 is present| 0 is ausent

# Add a column to Original Subseted Data with this information and then filter only thos present:
  
Meta_GloBi_I <- Subset_One %>% 
  bind_cols(In_EEZ_Mex) %>% 
    filter(EEZ == 1)  %>% 
    select(-EEZ)

```


## Observations
- The final table returns 824 observations which seem like a very small number
- The **r get_interactions_by_taxa** function gave me 1024 for both *Animalia* and *Plantae* which makes me think it has some kind of limit.
