---
title: "Reference List of the Metadata of Marine Research in Mexico"
date: "17/12/2016"
author: "Juliano Palacios Abrantes"
output:
  html_document:
    theme: lumen
    toc: yes
    toc_depth: '2'
  pdf_document:
    number_sections: no
    toc: yes
    toc_depth: 2
---

```{r Library, echo=F, eval=T, message=F, warning=F}
library(knitr)
library(dplyr)
library(readr)
```


```{r Loading Database, echo=F, eval=F, warning=F,message=F}
x <- read.csv("/Users/jpalacios/Documents/Github/Meta_Data_Mexico/App/Data/Reference.csv") 
x <- x %>% 
  group_by(Nombre)
#kable(x)


# x <- read_csv("~/Documents/Github/Meta_Data_Mexico/App/Data/Reference.csv") 
# x <- x %>% 
#   group_by(Nombre)

#head(x[2])
References <- levels(x$Nombre)


  
```

```{r Reference Template, echo=F, eval=F}

#Tis is the reference template. Add a new template for each new reference added to the metadata. Change "Template" for the next number....

Ref_Template <- References[Template]
ReferenceTemplate  <- x %>% 
  filter(Nombre == Ref_Template) %>% 
  slice(1) %>% 
  select(
         Nombre,
         Org,
         Acceso,
         Year
         )
  
Summary_Template <- kable(align ="c",
                   col.names = c("Compilation","Org","Institution","Publication Year"),
                   ReferenceTemplate)

Cita_Template <- x %>% 
  filter(Nombre == Ref_Template) %>% 
  slice(1) %>% 
  select(Repositorio,
         Org)
                    
Link_Template <- paste(Cita_Template$Org,Cita_Template$Repositorio)

## Copy and paste the following part outside the chunk

#`r Ref_Template`

`r Summary_Template`

### Abstract


### Link

`r Link_Template`

```



# Introduction
This list is made based on the *"Compilation Title"* variable of the metadata. As explained in the *"Protocol"*, the *Compilation Title* is a category that englobes different data in one webpage, book, or report.

\clearpage

```{r Reference 1 CONAPESCA, echo=F, eval=T, warning=F,message=F}

Ref_1 <- References[1]
Reference1  <- x %>% 
  filter(Nombre == Ref_1) %>% 
  slice(1) %>% 
  select(
         Nombre,
         Org,
         Acceso,
         Year
         )
  
Summary_1 <- kable(align ="c" ,col.names = c("Compilation","Institution","Access","Publication Year"),Reference1)

Cita_1 <- x %>% 
  filter(Nombre == Ref_1) %>% 
  slice(1) %>% 
  select(Repositorio,
         Org)

Abstract_1 <- x$Resumen[1]

                    
Link_1 <- paste(Cita_1$Org,Cita_1$Repositorio)

```

#`r Ref_1`


`r Summary_1`

### Abstract
`r Abstract_1`


### Link

`r Link_1`


```{r Reference 2 CONAPESCA, echo=F, eval=T, warning=F,message=F}

Ref_2 <- References[2]
Reference2  <- x %>% 
  filter(Nombre == Ref_2) %>% 
  slice(1) %>% 
  select(
         Nombre,
         Org,
         Acceso,
         Year
         )
  
Summary_2 <- kable(align ="c" ,col.names = c("Compilation","Institution","Access","Publication Year"),Reference2)

Cita_2 <- x %>% 
  filter(Nombre == Ref_2) %>% 
  slice(1) %>% 
  select(Repositorio,
         Org)

Abstract_2 <- x %>% 
  filter(Nombre == Ref_2) %>% 
  select(Resumen)

                    
Link_2 <- paste(Cita_2$Org,Cita_2$Repositorio)

```

#`r Ref_2`

`r Summary_2`

### Abstract
`r Abstract_2`


### Link

`r Link_2`

```{r Reference 3 CONABIO, echo=F, eval=T, warning=F,message=F}


Ref_3 <- References[3]
Reference3  <- x %>% 
  filter(Nombre == Ref_3) %>% 
  slice(1) %>% 
  select(
         Nombre,
         Org,
         Acceso,
         Year
         )
  
Summary_3 <- kable(align ="c" ,Reference3,
                   col.names = c("Compilation","Org","Institution","Publication Year"))

Cita_3 <- x %>% 
  filter(Nombre == Ref_3) %>% 
  slice(1) %>% 
  select(Repositorio,
         Org)

Abstract_3 <- x$Resumen[3]

                    
Link_3 <- paste(Cita_3$Org,Cita_3$Repositorio)

```

#`r Ref_3`

`r Summary_3`

### Abstract
`r Abstract_3`


### Link

`r Link_3`

```{r Reference 4 DataMares, echo=F, eval=T, warning=F,message=F}


Ref_4 <- References[4]
Reference4  <- x %>% 
  filter(Nombre == Ref_4) %>% 
  slice(1) %>% 
  select(
         Nombre,
         Org,
         Acceso,
         Year
         )
  
Summary_4 <- kable(align ="c" ,col.names = c("Compilation","Org","Institution","Publication Year"),Reference4)

Cita_4 <- x %>% 
  filter(Nombre == Ref_4) %>% 
  slice(1) %>% 
  select(Repositorio,
         Org)

Abstract_4 <- x$Resumen[4]

                    
Link_4 <- paste(Cita_4$Org,Cita_4$Repositorio)

```

#`r Ref_4`

`r Summary_4`

### Abstract
`r Abstract_4`


### Link

`r Link_4`

```{r Reference 5 MMM, echo=F, eval=T, warning=F,message=F}


Ref_5 <- References[5]
Reference5  <- x %>% 
  filter(Nombre == Ref_5) %>% 
  slice(1) %>% 
  select(
         Nombre,
         Org,
         Acceso,
         Year
         )
  
Summary_5 <- kable(align ="c" ,col.names = c("Compilation","Org","Institution","Publication Year"),Reference5)

Cita_5 <- x %>% 
  filter(Nombre == Ref_5) %>% 
  slice(1) %>% 
  select(Repositorio,
         Org)

Abstract_5 <- x$Resumen[5]

                    
Link_5 <- paste(Cita_5$Org,Cita_5$Repositorio)

```

#`r Ref_5`

`r Summary_5`

### Abstract

`r Abstract_5`


### Link

`r Link_5`

```{r Reference 6 SATMO, echo=F, eval=T, warning=F,message=F}


Ref_6 <- References[6]
Reference6  <- x %>% 
  filter(Nombre == Ref_6) %>% 
  slice(1) %>% 
  select(
         Nombre,
         Org,
         Acceso,
         Year
         )
  
Summary_6 <- kable(align ="c" ,col.names = c("Compilation","Org","Institution","Publication Year"),Reference6)

Cita_6 <- x %>% 
  filter(Nombre == Ref_6) %>% 
  slice(1) %>% 
  select(Repositorio,
         Org)

Abstract_6 <- x$Resumen[6]
                    
Link_6 <- paste(Cita_6$Org,Cita_6$Repositorio)

```

#`r Ref_6`

`r Summary_6`

### Abstract
`r Abstract_6`

### Link
`r Link_6`

```{r Reference 7 SAU, echo=F, eval=T, warning=F,message=F}


Ref_7 <- References[7]
Reference7  <- x %>% 
  filter(Nombre == Ref_7) %>% 
  slice(1) %>% 
  select(
         Nombre,
         Org,
         Acceso,
         Year
         )
  
Summary_7 <- kable(align ="c",
                   col.names = c("Compilation","Org","Institution","Publication Year"),
                   Reference7)

Cita_7 <- x %>% 
  filter(Nombre == Ref_7) %>% 
  slice(1) %>% 
  select(Repositorio,
         Org)

Abstract_7 <- x$Resumen[7]
                    
Link_7 <- paste(Cita_7$Org,Cita_7$Repositorio)

```

#`r Ref_7`

`r Summary_7`

### Abstract
`r Abstract_7`

### Link

`r Link_7`

```{r Reference 8, echo=F, eval=T, warning=F,message=F}

#Tis is the reference 8. Add a new 8 for each new reference added to the metadata. Change "8" for the next number....

Ref_8 <- References[8]
Reference8  <- x %>% 
  filter(Nombre == Ref_8) %>% 
  slice(1) %>% 
  select(
         Nombre,
         Org,
         Acceso,
         Year
         )
  
Summary_8 <- kable(align ="c",
                   col.names = c("Compilation","Org","Institution","Publication Year"),
                   Reference8)

Cita_8 <- x %>% 
  filter(Nombre == Ref_8) %>% 
  slice(1) %>% 
  select(Repositorio,
         Org)

Abstract_8 <- x$Resumen[8]
                    
Link_8 <- paste(Cita_8$Org,Cita_8$Repositorio)

```

#`r Ref_8`
`r Summary_8`

### Abstract
`r Abstract_8

### Link

`r Link_8`