---
title: "Instructions for the Meta Database of Marine Research"
output:
  pdf_document:
    fig_height: 2
    fig_width: 2
    number_sections: no
    toc: yes
    toc_depth: 2
  html_document:
    fig_height: 2
    fig_width: 2
    theme: lumen
    toc: yes
    toc_depth: '2'
Author: "Juliano Palacios Abrantes"
---

#General Guidence

The following document contains the instructions to add information on the meta-database of marine research in Mexico. The database has 27 categories to be filled by the user, please note that not all of them are mandatory. However, we encourage you to fill as much as possible. The more information we have the better we will be able to reflect the state of marine research in Mexico!

All fields have one of four non-exclusive possible characteristics:

1. They can be *Mandatory* or *Optional*
2. They can be *Fixed* values or open *Section*
    + Fixed: the inputs are part of a select group and no other value is allowed
    + Open: Inputs can be whatever the author decides

3. There could be *Multiple Values* or a *Single One*

Please consider the following directions as general rules for all categories:

- Do not include accents or special characters (e.g. ñ, ç, etc.)
- Overall, entries can be in both Spanish and/or English (except stated otherwise)
- Separate words (e.g. keywords) by ";" and not by "," or blank spaces.
- If you have the same data for multiple species, each species should be a different row

#### Contact Information

For any inquiry regarding data input feel free to contact Juliano Palacios (j.palacios@oceans.ubc.ca). More information about the project, the metadata, and preliminary results can all be found on our [Website](https://jepa.shinyapps.io/marmetadatamexeng/)


```{r Template, echo =F, eval=T, message=F, warning=F}
suppressWarnings(library(dplyr))
suppressWarnings(library(data.table))
Data <- fread("~/Documents/Github/Meta_Data_Mexico/App_Eng/Template.csv")

```

#Metadata Fields

<!-- ##MMID -->
<!-- - Mandatory / Fixed / Single -->

<!-- This is the ID of each data entry. It is important to input this number correcly after the last data point to keep consistency. -->

##Short Title
- Mandatory / Open / Single

Short informative title of the data set. There are no limitations on the number of words but it should be as informative as possible.

###Example
*MMID_361:* "Catch of Thunnus alalunga in Mexico (Atlantic)"
*Original dataset title:* SAU eeZ 944 v1-43

##Keywords
- Mandatory / Open / Multiple / Spanish

Words in Spanish that best describe the subject or/and data set. These words will be useful to search data. There is no words limitation. Can be both words and numbers.

**Special Situation:** When a row contains more than one data-sets the keywords must have all the data-sets available in the repository. 

###Example
For a "normal" row, the keywords could look something like this:

- *MMID_361:* Captura; Reconstruida; Atlantico; Industrial; Subsistencia; Artesanal; Deportiva; Thunnus alalunga

**Special Situation:**  A good example for this section is *MMID_105* where the Short Title of the data set is "Historic Catch of Calamari for Multiple States". In this case, the original data set has catch for five different states in Mexico. Hence the keywords: *"Calamar; Captura; Campeche; Colima; Oaxaca; Yucatan; Quintana Roo"*

```{r MMID:Keywords 1, echo =F, eval=T}

suppressWarnings(library(knitr))

#Data <- read.csv("./Template.csv")

D <- Data %>%
  filter(MMID == 361|
         MMID == 105) %>% 
  select(1:3)

kable(head(D[2:3],5),
      format = "markdown",
      caption = "Spreadsheet View of Examples for Short Title and Keywords")
      

```

##Author
- Mandatory / Open / Multiple

Principal (first) author of the data set. The author can be a person, group or organization. However, priority must me given to individuals over groups or institutions. In case of multiple authors, an additional *"et al."* should be included after the first author. Do not include all authors. In case there is no information about the author of the data set, whoever is uploading the data should be referenced as author.

###Examples
- *MMID_361:* Andres Cisneros-Montemayor
- *MMID_613:* CONABIO
- *MMID_712:* Acosta-Gonzalez, G.; et.al

##Institution
- Optional / Open / Single

Institution where the data set lives. In the case of multiple institution provide the one that serves as an umbrella. Please use abbreviations when possible.

###Example
- *MMID_361:* SAU (Sea Around Us)
- *MMID_19:* CONAPESCA (even thou CONAPESCA is part of SAGARPA and the Mexican Government, the data lives on CONAPESCA's web page)


##Dataset Available
- Mandatory / Fixed / Single

Is the data set available for consultation or download. This section is numeric and the options are:

1.	Yes, it is public domain and available for consultation and/or download
2.	Yes, it is public domain. However, is not directly available or has some type of limitation (nationality, request, broken link, or is just absent)
 3.	No, it is a private data set

###Examples
- *MMID_361:* 1, The data set is available for download online
- *MMID_1198:* 2, In this case the data set is public domain (Mexican government). However, it is limited to Mexicans and its access is only upon request.
- *MMID_1523:* 3, The metadata is available however, the data is not available. A contact information is provided for further inquiries.

##Subject Name
- Mandatory / Open / Single (two words) / Spanish

This category comprehends the name of the principal subject of the data set. In case of species, priority should be given to scientific names (without author and year). In case the scientific name is unknown the common name should be included in Spanish. All entries should be in Spanish, with the clear exception of scientific names.

###Example
- *MMID_361:* Thunnus alalunga
- *MMID_19:* Abulon 
- *MMID_1198:* Chiapas

```{r Author:SubjectName 1, echo =F, eval=T}

suppressWarnings(library(knitr))
#Data <- read.csv("./Template.csv")

D2 <- Data %>%
  filter(MMID == 361|
           MMID == 613|
           MMID == 712|
           MMID == 19|
           MMID == 1198|
           MMID == 1523|
         MMID == 105) %>% 
  select(1,4:7)

kable(head(D2),
      format = "markdown",
      caption = "Spreadsheet View of Examples for Author, Intitution, Dataset Available, and Subject Name")

```


##Area
- Mandatory / Fixed / Single

The broader category of where the data was generated. Fixed options are as follows:
-	National (When data applies for the whole country or scatter data from both oceans)
- Atlantic Ocean (Covers the Gulf of Mexico and Caribbean)
- Pacific Ocean (Any part within Mexico's Pacific Ocean)
- Freshwater/Terrestrial (When data is related to freshwater and/or land ecosystems)

##Region
- Mandatory / Fixed / Single

A less broad location of the data. While this option is mandatory, the option of "NA" (Not Applicable) is valid. However, authors are encourage to select one of the following options:

-	Gulf of California
-	Northwest Pacific
-	South Pacific
-	Gulf of Tehuantepec
-	Yucatan Peninsula / Mar Caribe
-	West Gulf of Mexico.



**Special Situation**: When data is spread and located in more than one region, authors should act as follow:
a. If data is spread within two contiguous locations, author should choose the one that has the more amount of data
b. If data is spread within two areas that are not connected, then the category should be "NA"

### Example (Special Situation)

- **MMID_630:** In this case the author decided to categorize this data as "Gulf of Tehuantepec" since it covers that whole area and only partial "South Pacific"

- **MMID_636:** For this data set Region was determined as "NA" since the data is spread out the country's coastal line.

##Location
- Optional / Open / Single
The more specific level of data localization. It can range from a specific state to georeferenced data. It is an open category with no limitations.

###Example
- *MMID_1198:* Chiapas
- *MMID_1248:* Georeference
- *MMID_606:* Laguna de Terminos

##Start and End Year
- Mandatory / Open / Single
The Starting year and end year of the time series.

** Special Situation:** When the row represents multiple data set with different time frames, the section should be "NA" (MMID_612)

##Temporal Resolution
- Mandatory / Fixed / Single
What is the temporal resolution of the data? The options are as follows:
-	Annual
-	Monthly
-	Semester
-	Weekly
-	Daily
-	Seconds

** Special Situation:** Likewise Location

##Data Time Points
- Mandatory / Open / Single
This section refers to the amount of data points available in the data set. It is related to the start and end year.

**Special Situation:** In the case of multiple data-sets within a row, Data Time Points should reflect the amount of data-sets within that row. 


###Example
**MMID_361:** 55. The data set starts in 1952 and ends in 2010, hence, there are 52 data-points.
**MMID_377:** 5. The data set starts in 1954 and ends in 1966, however, there are only 5 years with data and not 13. 

**Special Situation: MMID_377**, has 117 different data-sets regarding socioeconomic information. Hence, while the name is only on data set, the number of data time points become 117.

```{r Area:DTPoints 1, echo =F, eval=T}

suppressWarnings(library(knitr))
#Data <- read.csv("./Template.csv")

D <- Data %>%
  filter(MMID == 630|
           MMID == 636|
           MMID == 1198|
           MMID == 1248|
           MMID == 606|
           MMID == 362|
         MMID == 377) %>% 
  select(1,8:13)

kable(head(D,7),
      format = "markdown",
      caption = "Spreadsheet View of Examples for Area, Region, Location, Start and End years, and amount of datapoints")

```


##Unit Type
- Mandatory / Fix / Single
They type of unit presented in the data set. The options are:
- Area
- Size
- Weight
- Values
- Counts
- Index
- Temperature
- Concentration
- pH
- Depth

##Temporal Resolution
- Mandatory / Fix / Single

What is the temporal resolution of the data set.

### Example

*MMID_361:* Year
*MMID_1266:* Month

##Spatial Resolution
- Optional / Fix / Single

What is the spatial resolution of the data set.

### Example

*MMID_361:* Area 
*MMID_1266:* National

```{r UntiType:DatasetTitle 1, echo =F, eval=T}

suppressWarnings(library(knitr))
#Data <- read.csv("./Template.csv")

D <- Data %>%
  filter(MMID == 361|
           MMID == 1266
           ) %>% 
  select(1,14:16)

kable(head(D),
      format = "markdown",
      caption = "Spreadsheet View of Examples for Unit Type, and Temporal and Spatial Resolution")

```

##Dataset Title
- Mandatory / Open / Single

Original name of data set (the data specifically, not the source or repository where it was published). This is important in order to localize the data set in a document or a source that has multiple data-sets.

### Example
**MMID_1266:** The name of the row is:"*Valor mensual de Importacion de Productos Pesqueros en (2014)*" but the name of the original data set is *"Exportacion de Productos Pesqueros y Acuicolas 2014/p"*

##Compilation Title
- Mandatory[^1] / Open / Single

[^1]: When applicable

### Definition
in case the data is part of a larger aggregation of data, for example a report or a repository, then the name of the report / repository should be included.

### Example

- Fish Base
- Anuario Estadístico SAGARPA
- Censo Poblacional de INEGI

These are all mayor aggregations/sources of data

```{r Data_Title:CompTitle, echo =F, eval=T}

suppressWarnings(library(knitr))
#Data <- read.csv("./Template.csv")

D <- Data %>%
  filter(MMID == 361|
           MMID == 1266
           ) %>% 
  select(1,17:18)

kable(head(D),
      format = "markdown",
      caption = "Spreadsheet View of Examples for Dataset and Compilation Title")

```

##Publication Year
- Open / Single

Year in which the data set was published or made available for consultation. Note that this is not the sames as when the data was collected.

##Reference
Link or address of where the data can be found. In case of scientific articles please include only the DOI (if available), otherwise, include the whole citation. For thesis or gray literature that can't be found on-line, include the physical reference.

### Example
- www.repositoryonlinewheredatalives.com  

- http://doi.org/10.1016/j.gloenvcha.2015.03.009

<!-- ##Available in Metadata -->
<!-- If the data is or not part of the Meta-dataset data repository -->

<!-- ##Metadata Name -->
<!-- In case the data set is in the Meta-data, then what's the name of it? -->

##User Contact
- Mandatory / Open / Single

Name and email of person who identified and/or added the data to the Metadata

##Institution Type
- Optional / Fix / Single

The type of institution that generated the data set (corresponds to "Author" and/or Institution" fields). Options are:

- Academic
- Government (GOV)
- Non-Governmental Organization (NGO)
- Inter-Governmental Organization (IGO)
- Industry (Industry)
- Private (Private)

```{r PublicationYear:InstType, echo =F, eval=T}

suppressWarnings(library(knitr))
#Data <- read.csv("./Template.csv")

D <- Data %>%
  filter(MMID == 361
           ) %>% 
  select(1,19,22:24)

kable(head(D))

```

##Research Fund
- Optional / Fix / Single

When possible, please identify what type of organization funded the research. This defers on the Institution Type since sometimes who carries on the research is not the same body that funds it.  

Options Are:

- Academic
- Government (GOV)
- Non-Governmental Organization (NGO)
- Inter-Governmental Organization (IGO)
- Industry (Industry)
- Private (Private)


##Research Field
- Optional / Fix / Single
What was the main reason why the data was  gathered. Note, this section refers to the "suject_name" and even thou data could be, for example, economic, the subject could be a fishery.  

Options Are:

- Fisheries
- Aquaculture
- Tourism
- Oceanography
- Conservation
- Sociology (includes economic data)
- Biology (Includes ecological or natural science data)

### Example:

*MMID_1756:* Financiamiento al sector pesquero (2004-2013) is actually a "Fisheries" category because the *Subject_Name* is "Sector Pesquero".

*MMID_8:* Censo Poblacion y Vivienda 2010 is a "Sociology" category
*MMID_1502:* Poblacion Total Escenario de Cambio Climatico A2, 2030

##Social-Economic Interaction
- Optional / Fix / Single

What type of social-ecological interaction is this data an indicator of. It also refers to the Subject_name.

Options are:

- Benefit (Catch or Landed value)
- State (Stock assessment or Habitat area)
- Pressure (Fishing effort)
- Response (CONAPESCA budget or Protected area coverage)

### Example:

*MMID_8:* State (is evaluating the amount of people living in an area)
*MMID_1756:* In this case the *SE_Interaction* is "Pressure" because the *Subject_name* is "Sector Pesquero". The fund is for fishing (subsidies).


```{r RFund:SEI, echo =F, eval=T}

suppressWarnings(library(knitr))
#Data <- read.csv("./Template.csv")

D <- Data %>%
  filter(MMID == 1756|
           MMID == 8|
           MMID == 15002
           ) %>% 
  select(1:2,7,26:27)

kable(head(D))

```


<!-- ##Data-Uncertanty -->
<!-- What is the quality of the data? -->
